
%Tex File: c:/Dropbox/PublicData/LocalLaborMarketsInCanadaAndTheUnitedStates/Rprograms5/20-Bartik_China_Regressions/TexFiles/20-bartik_2sls.tex

% Date and time: Sun, Mar 10, 2019 - 10:36:43 PM
\begin{sidewaystable}[!htbp] \centering 
  \caption{2SLS Estimates -- Local Labor Market Effects of Sectoral Shifts Predicted at the National Level (Bartik):  1990 to 2011} 
  \label{tab:bartik_2sls} 
\small
\begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{11}{c}{\textit{Dependent variable: Difference in }} \\ 
\cline{2-12} 
\\[-2.0ex]
 & Wage & Log & Log & Log & Log & Wage & Log & Log & Log & Log & Log \\
 & Location & Popu- & Emp/Pop & Unemp & Unemp. & Skill & Foreign/ & Univ/ & Univ/HS & 90/10 & Housing \\
 & Index & lation & Ratio & Rate & Insurance & Index & Pop & Pop & Wage & Wage & Cost \\
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11)\\ 
\hline \\[-1.8ex] 
 $\Delta$ Log Employment $\times$ & 0.533$^{***}$ & 0.581$^{***}$ & 0.419$^{***}$ & $-$3.285$^{***}$ & $-$3.782$^{**}$ & $-$0.258$^{***}$ & $-$0.634 & 0.005 & 0.131 & 0.359 & 1.653$^{***}$ \\ 
United States  & (0.118) & (0.090) & (0.090) & (0.755) & (1.542) & (0.052) & (0.796) & (0.032) & (0.104) & (0.240) & (0.352) \\ 
  & & & & & & & & & & & \\ 
 $\Delta$ Log Employment $\times$ & 0.561$^{***}$ & 0.816$^{***}$ & 0.184$^{***}$ & $-$2.191$^{***}$ & $-$1.703$^{**}$ & $-$0.227$^{***}$ & 1.545$^{***}$ & 0.171$^{***}$ & 0.178 & 0.163 & 0.097 \\ 
Canada  & (0.063) & (0.066) & (0.066) & (0.370) & (0.723) & (0.034) & (0.253) & (0.031) & (0.163) & (0.146) & (0.324) \\ 
  & & & & & & & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 1,038 & 1,038 & 1,038 & 1,038 & 966 & 1,038 & 1,038 & 1,038 & 1,038 & 1,038 & 1,038 \\ 
US = CA p-value & 0.831 & 0.035 & 0.035 & 0.193 & 0.223 & 0.625 & 0.009 & 0.000 & 0.809 & 0.487 & 0.001 \\
\hline 
\hline \\[-1.8ex] 
\end{tabular} 
\begin{tablenotes}
\footnotesize
\item \textit{Notes:} See the notes for table \ref{tab:gradients}. Sample consists of 264 metro areas in the United States and 82 in Canada observed  in  1990, 2000, 2007, and 2011. Not all dependent variables are available for all metro areas. The CBP/ASM Bartik instrument is calculated using County (US) Businesss Patterns or Canadian (CA) Business Patterns along with the ASM data, respectively. The Bartik instruments are calculated using the start of sample as the base year. Within each panel, controls include decadal and census division/region fixed effects. The p-value in the bottom row is associated with the null hypothesis of equality on the coefficients ($\Delta$ Log Employment) across the United States and Canada. See the notes to table \ref{tab:summ_stats} for data sources and definitions. Regressions are  weighted by start of period population 24-59. Heteroskedasticity robust standard errors clustered at the state/province level and are in parentheses. *, **, *** indicates statistical significance at the 10, 5, and 1 percent levels, respectively.
\end{tablenotes}
\end{threeparttable}
\end{sidewaystable} 



