
%Tex File: c:/Dropbox/PublicData/LocalLaborMarketsInCanadaAndTheUnitedStates/Rprograms5/20-Bartik_China_Regressions/TexFiles/21-bartik_2sls_common_city_sizes.tex

% Date and time: Sun, Mar 10, 2019 - 10:36:44 PM
\begin{sidewaystable}[!htbp] \centering 
  \caption{2SLS Common City Size Estimates of Changes in Local Labor Market Outcomes due to Changes in Employment (Two Bartik Instrument Estimates): 1990 to 2011} 
  \label{tab:bartik_2sls_common} 
\small
\begin{threeparttable}
\begin{tabular}{@{\extracolsep{5pt}}lccccccccccc} 
\\[-1.8ex]\hline 
\hline \\[-1.8ex] 
 & \multicolumn{11}{c}{\textit{Dependent variable: Difference in }} \\ 
\cline{2-12} 
\\[-2.0ex]
 & Wage & Log & Log & Log & Log & Wage & Log & Log & Log & Log & Log \\
 & Location & Popu- & Emp/Pop & Unemp & Unemp. & Skill & Foreign/ & Univ/ & Univ/HS & 90/10 & Housing \\
 & Index & lation & Ratio & Rate & Insurance & Index & Pop & Pop & Wage & Wage & Cost \\
\\[-1.8ex] & (1) & (2) & (3) & (4) & (5) & (6) & (7) & (8) & (9) & (10) & (11)\\ 
\hline \\[-1.8ex] 
 $\Delta$ Log Employment $\times$ & 0.447$^{***}$ & 0.634$^{***}$ & 0.366$^{***}$ & $-$2.799$^{***}$ & $-$2.277$^{***}$ & $-$0.198$^{***}$ & $-$0.574 & $-$0.006 & $-$0.061 & 0.008 & 1.501$^{***}$ \\ 
United States  & (0.085) & (0.058) & (0.058) & (0.486) & (0.613) & (0.037) & (0.672) & (0.022) & (0.054) & (0.126) & (0.347) \\ 
  & & & & & & & & & & & \\ 
 $\Delta$ Log Employment $\times$ & 0.679$^{***}$ & 0.756$^{***}$ & 0.244$^{**}$ & $-$2.601$^{***}$ & $-$1.932$^{**}$ & $-$0.294$^{***}$ & 1.535$^{***}$ & 0.177$^{***}$ & 0.254 & 0.128 & 0.140 \\ 
Canada  & (0.123) & (0.106) & (0.106) & (0.708) & (0.767) & (0.055) & (0.367) & (0.036) & (0.252) & (0.191) & (0.388) \\ 
  & & & & & & & & & & & \\ 
\hline \\[-1.8ex] 
Observations & 927 & 927 & 927 & 927 & 883 & 927 & 927 & 927 & 927 & 927 & 927 \\ 
US = CA p-value & 0.121 & 0.316 & 0.316 & 0.818 & 0.726 & 0.145 & 0.006 & 0.000 & 0.223 & 0.600 & 0.009 \\
\hline 
\hline \\[-1.8ex] 
\end{tabular} 
\begin{tablenotes}
\footnotesize
\item \textit{Notes:} See the notes for table \ref{tab:gradients}. Sample consists of 255 metro areas in the United States and 54 in Canada observed in 1990, 2000, 2007, and 2011. Not all dependent variables are available for all metro areas. The CBP/ASM Bartik instrument is calculated using County (US) Businesss Patterns or Canadian (CA) Business Patterns along with the ASM data, respectively. The Bartik instruments are calculated using the start of sample as the base year. Within each panel, controls include decadal and census division/region fixed effects. Cities are chosen so that 1990 24-59 city population size has a common support. The p-value in the bottom row with the null hypothesis of equality on the coefficients ($\Delta$ Log Employment) across the United States and Canada. See the notes to table \ref{tab:summ_stats} for data sources and definitions. Regressions are  weighted by start of period population 24-59. Heteroskedasticity robust standard errors clustered at the state/province level and are in parentheses. *, **, *** indicates statistical significance at the 10, 5, and 1 percent levels, respectively.
\end{tablenotes}
\end{threeparttable}
\end{sidewaystable} 



